Croder \\ Bringing the Knowledge of the Crowds into the IDE

### 2013-05-03 paper/paper.tex
Added bibliography
A small database with only 4 references.
Added more info to the general CrowdSourcing section
Again, this is for issue #24

\documentclass[]{sigchi}

@@

Mechanical Turk tasks tend to be very simple and require only minimal knowledge and cognitive
skills. During one experiment we asked a technical question about JavaScript. Out of the 10 hits,
9 were complete in 7 days. This partly shows that the Mechanical Turk platform is ill-suited for tasks
that require a lot of specialized knowledge.

@@

@@

>>>>

\documentclass{sigchi}

@@

Mechanical Turk tasks tend to be very simple and require only minimal knowledge and cognitive
skills. During one experiment we asked a technical question about JavaScript. Out of the 10 hits,
9 were complete in 7 days. Of those 9 tasks, only 4 useful and most of them were incomplete. This partly 
shows that the Mechanical Turk platform is ill-suited for tasks that require specialized knowledge.

@@

StackOverflow\footnote{\url{http://www.stackoverflow.com}} allow uses to post questions and get
answers. The service is larger than most social Q\&A and technical forums. With a median answer time 
of 11 minutes and a very active user user base \cite{Mamykina2011} it makes a good candidate for a
platform to run the experiment. StackOverflow is part of a network of sites (StackExchange\footnote{\url{http://www.stackexchange.com}} that follow the same modes. One of them, \emph{Code
Review Stack Exchange}\footnote{\url{http://codereview.stackexchange.com}} is based around the
concept of concept of code review. It is this platform that we have used to test our protype.

@@

\bibliographystyle{acm-sigchi}
\bibliography{paper}
